---
title: "LSR3 analysis: effects of TAAR1 agonists in animal models of psychosis"
author: "Francesca Tinsdeall, Fiona Ramage, Virginia Chiocchia and Malcolm Macleod"
date: "2023-12-19"
output: html_document
bibliography: grateful-refs.bib
editor_options: 
  chunk_output_type: console
---

# Contents

1.  Flow of study selection

2.  Description of experiment types

    -   2.1 Simple interventions

3.  Risk of bias and reporting quality assessment

    -   3.1 Simple interventions

        -   3.1.1 Outcome 1: Locomotor activity

            -   3.1.1.1 Risks of bias

            -   3.1.1.2 Reporting quality

        -   3.1.2 Outcome 2: Prepulse inhibition

            -   3.1.2.1 Risks of bias

            -   3.1.2.2 Reporting quality

        -   3.1.3 Outcome 3: Cognition

            -   3.1.3.1 Risks of bias

            -   3.1.3.2 Reporting quality

        -   3.1.4 Outcome 4: Social interaction

            -   3.1.4.1 Risks of bias

            -   3.1.4.2 Reporting quality

        -   3.1.5 Outcome 5: Stereotypy

            -   3.1.5.1 Risks of bias

            -   3.1.5.2 Reporting quality

4.  Meta-analyses by experiment type and outcome

    -   4.1 Simple interventions (TAAR1 Agonist v Control)

        -   4.1.1 Outcome 1: Locomotor activity

        -   4.1.2 Outcome 2: Cognition

    -   4.2 "Head to head" interventions (TAAR1 Agonist v conventional antipsychotic)

        -   4.2.1 Outcome 1: Locomotor activity

        -   4.2.2 Outcome 2: Cognition

    -   4.3 "Positive control" (Conventional antipsychotic v control)

        -   4.3.1 Outcome 1: Locomotor activity

        -   4.3.2 Outcome 2: Cognition

    -   4.4 Combination treatment (TAAR1 Agonist plus conventional antipsychotic v conventional antipsychotic alone)

        -   4.4.1 Outcome 1: Locomotor activity

        -   4.4.2 Outcome 2: Cognition

5.  Subgroup analyses

    -   5.1 Simple interventions

        -   5.1.1 Outcome 1: Locomotor activity

            -   5.1.1.1 Sex

            -   5.1.1.2 Category of disease induction

            -   5.1.1.3 Route of intervention administration

            -   5.1.1.4 Prophylactic or therapeutic intervention

            -   5.1.1.5 Duration of treatment period

            -   5.1.1.6 The intervention administered

            -   5.1.1.7 The efficacy of the drug

            -   5.1.1.8 The selectivity of the drug

            -   5.1.1.9 Potency of intervention

            -   5.1.1.10 Dose of intervention

            -   5.1.1.11 SYRCLE RoB assessment

            -   5.1.1.12 ARRIVE reporting quality guidelines

            -   5.1.1.13 Heterogeneity explained by covariates

        -   5.1.2 Outcome 2: Cognition

            -   5.1.2.1 Sex

            -   5.1.2.2 Category of disease induction

            -   5.1.2.3 Route of intervention administration

            -   5.1.2.4 Prophylactic or therapeutic intervention

            -   5.1.2.5 Duration of treatment period

            -   5.1.2.6 The intervention administered

            -   5.1.2.7 The efficacy of the drug

            -   5.1.2.8 The selectivity of the drug

            -   5.1.2.9 Potency of intervention

            -   5.1.2.10 Dose of intervention

            -   5.1.2.11 SYRCLE RoB assessment

            -   5.1.2.12 ARRIVE reporting quality guidelines

            -   5.1.2.13 Heterogeneity explained by covariates

6.  Sensitivity Analyses

    -   6.1 Sensitivity analyses for simple interventions

        -   6.1.1 Locomotor activity

            -   6.1.1.1 Studies with low overall risk of bias

            -   6.1.1.2 Imputed rho values

            -   6.1.1.3 NMD

        -   6.1.2 Cognition

            -   6.1.2.1 Studies with low overall risk of bias

            -   6.1.2.2 Imputed rho values

            -   6.1.2.3 NMD

7.  Reporting bias/small study effects

    -   7.1 Egger regression

8.  Summary of the evidence

9.  Software used

```{r setup, message=F, echo=F, include=F}
### libraries
library(ggplot2)
library(devtools)
library(dosresmeta)
library(dplyr)
library(grid)
library(gtools)
library(kableExtra)
library(knitr)
library(Matrix)
library(meta)
library(metafor)
library(orchaRd)
library(readxl)
library(readr)
library(rje)
library(rms)
library(stringr)
library(tibble)
library(tidyr)
library(tools)
library(rlang)
devtools::install_github("mcguinlu/robvis")
install_github("mcguinlu/robvis")
library(robvis)
library(PRISMA2020)
library(grateful)


#define LSR
LSR <- 'LSR3'
# define date of processing
DoP <- Sys.Date()


# All function needed to run this notebook (analyses, etc.) should be in a util.R file
source("util/util.R")

# obtain the data and prepare them for analysis - all data cleaning routines should be in this .R script 


source("wrangling/wrangling_functions.R", local = TRUE)
source("wrangling/data_wrangle_script.R")

#Round off results to two digits
options(scipen=100, digits=3)

# Import data
file2load <- paste0(LSR,'_clean_data_',DoP,'.csv')
df <- read_csv(file2load)

```

# 1. Flow of study selection

```{r article metadata, eval = TRUE, echo = FALSE}
# Retrieve article metadata omitted from 'clean_data.csv' and join 

article_metadata <- df %>% 
  select(StudyId, Title, Year) %>%
  distinct()
```

The flow of study selection is shown in Figure 1. Studies included were published between `r min(article_metadata$Year)` and `r max(article_metadata$Year)`. Overall, this analysis includes `r length(table(df$StudyId))` studies containing `r nrow(df)` comparisons.

**Figure 1**

```{r PRISMA flowchart, eval = TRUE, echo = FALSE, warning=FALSE, message=FALSE}
prisma_data <- read_csv("data/LSR3_prisma_211223.csv")
dfp <- PRISMA_data(prisma_data)
PRISMA_flowdiagram(dfp, interactive=FALSE, previous=FALSE, other=FALSE,
                    detail_databases=FALSE, detail_registers=FALSE, fontsize=12, font="Helvetica",
                    title_colour="Goldenrod1", greybox_colour="Gainsboro", main_colour="Black",
                    arrow_colour="Black", arrow_head="normal", arrow_tail="none", side_boxes=TRUE )

## what about reasons for exclusions of records? don't we have info on them?
```

References of included studies are located in the appendix. Included studies used `r length(table(df$ModelID))` unique disease model induction procedures.

# 2. Description of experiment types

Within the literature we identified 3 distinct categories of experimental interventions:

1.  **"Simple interventions"**. These were experiments investigating the effect of administering a TAAR1 agonist alone.

2.  **"Head to head"**. These were experiments investigating the effect of administering a TAAR1 agonist alongside a currently licensed anti-psychotic.

3.  **"TAAR1 antagonist experiments**. These were experiments investigating the effect of administering a TAAR1 agonist alongside TAAR1 antagonism. In this iteration of the review, all experiments within this category administered to TAAR1 knock-out animals (i.e. used genetic TAAR1 antagonism).

Each experiment type will be analysed separately. This is because each experiment type uses different control conditions.

## 2.1 Simple interventions

In "simple intervention" studies the:

-   **Control group** is a group of animals that is (1) subjected to a psychosis model induction paradigm and (2) administered a control treatment (vehicle) or no treatment

-   **Intervention group** is a group of animals that is (1) subjected to a psychosis model induction paradigm and (2) administered a TAAR1 agonist treatment

-   **Sham group** is a group of animals that is (1) not subjected to a psychosis model induction paradigm and (2) administered a control treatment (vehicle) or no treatment

```{r # Split df by experiment and outcome type into dataframes to simply inline code below - simple interventions, eval = TRUE, echo = FALSE}
df_S <- filter(df, SortLabel == "TvC")
df_S_LMA <- filter_experiment_outcome_type(df, "TvC", "Locomotor activity")
df_S_PPI <- filter_experiment_outcome_type(df, "TvC", "Prepulse inhibition")
df_S_cog <- filter_experiment_outcome_type(df, "TvC", "Cognition")
df_S_social <- filter_experiment_outcome_type(df, "TvC", "Social interaction")
df_S_stereo <- filter_experiment_outcome_type(df, "TvC", "Stereotypy")
```

`r length(table(df_S$StudyId))` studies (`r nrow(df%>%filter(SortLabel == "TvC"))` comparisons) investigated the effects of simple interventions. The number of studies and individual effect sizes for each outcome were:

-   Locomotor activity\*: `r length(table(df_S_LMA$StudyId))` studies and `r nrow(df_S_LMA)` comparisons in `r {strains <- unique(df_S_LMA$Strain); if (length(strains) > 1) paste(length(strains), "strains") else paste(length(strains), "strain")}`

-   Prepulse inhibition\*: `r length(table(df_S_PPI$StudyId))` studies and `r nrow(df_S_PPI)` comparisons in `r {strains <- unique(df_S_PPI$Strain); if (length(strains) > 1) paste(length(strains), "strains") else paste(length(strains), "strain")}`

-   Cognitive function: `r length(table(df_S_cog$StudyId))` studies and `r nrow(df_S_cog)` comparisons in `r {strains <- unique(df_S_cog$Strain); if (length(strains) > 1) paste(length(strains), "strains") else paste(length(strains), "strain")}`

-   Social interaction: `r length(table(df_S_social$StudyId))` studies and `r nrow(df_S_social)` comparisons in `r {strains <- unique(df_S_social$Strain); if (length(strains) > 1) paste(length(strains), "strains") else paste(length(strains), "strain")}`

-   Stereotypy: `r length(table(df_S_stereo$StudyId))` studies and `r nrow(df_S_stereo)` comparisons in `r {strains <- unique(df_S_stereo$Strain); if (length(strains) > 1) paste(length(strains), "strains") else paste(length(strains), "strain")}`

\* These outcomes were identified in the study protocol as primary outcomes of interest

# 3. Risk of bias and reporting quality assessment

## 3.1 Simple interventions

#### 3.1.1 Outcome 1 : Locomotor activity

##### 3.1.1.1 Risks of bias

Figure 3.1.1.1.1 shows the risk of bias summary for studies investigating the effect of administering a TAAR1 agonist on locomotor activity in animals. The risk of bias assessment was performed using the SYRCLE's RoB tool. Figure 3.1.1.1.2 shows the corresponding traffic light plot.

**Figure 3.1.1.1.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_summary(df, "TvC", "Locomotor activity")
```

**Figure 3.1.1.1.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_traffic(df, "TvC", "Locomotor activity")
```

##### 3.1.1.2 Reporting quality

Figure 3.1.1.2.1 shows the reporting quality summary for studies investigating the effect of administering a TAAR1 agonist on locomotor activity in animals. The reporting quality assessment was performed using the ARRIVE guidelines. Figure 3.1.1.2.2 shows the corresponding traffic light plot.

**Figure 3.1.1.2.1**

```{r warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_summary(df, "TvC", "Locomotor activity")
```

**Figure 3.1.1.2.2**

```{r message = FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_traffic(df, "TvC", "Locomotor activity")
```

#### 3.1.2 Outcome 2 : Prepulse inhibition

##### 3.1.2.1 Risks of bias

Figure 3.1.2.1.1 shows the risk of bias summary for studies investigating the effect of administering a TAAR1 agonist on prepulse inhibition in animals. The risk of bias assessment was performed using the SYRCLE's RoB tool. Figure 3.1.2.1.2 shows the corresponding traffic light plot.

**Figure 3.1.2.1.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_summary(df, "TvC", "Prepulse inhibition")
```

**Figure 3.1.2.1.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_traffic(df, "TvC", "Prepulse inhibition")
```

##### 3.1.2.2 Reporting quality

Figure 3.1.2.2.1 shows the reporting quality summary for studies investigating the effect of administering a TAAR1 agonist on prepulse inhibition in animals. The reporting quality assessment was performed using the ARRIVE guidelines. Figure 3.1.2.2.2 shows the corresponding traffic light plot.

**Figure 3.1.2.2.1**

```{r warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_summary(df, "TvC", "Prepulse inhibition")
```

**Figure 3.1.2.2.2**

```{r message = FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_traffic(df, "TvC", "Prepulse inhibition")
```

#### 3.1.3 Outcome 3 : Cognition

##### 3.1.3.1 Risks of bias

Figure 3.1.3.1.1 shows the risk of bias summary for studies investigating the effect of administering a TAAR1 agonist on cognition in animals. The risk of bias assessment was performed using the SYRCLE's RoB tool. Figure 3.1.3.1.2 shows the corresponding traffic light plot.

**Figure 3.1.3.1.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_summary(df, "TvC", "Cognition")
```

**Figure 3.1.3.1.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_traffic(df, "TvC", "Cognition")
```

##### 3.1.3.2 Reporting quality

Figure 3.1.3.2.1 shows the reporting quality summary for studies investigating the effect of administering a TAAR1 agonist on cognition in animals. The reporting quality assessment was performed using the ARRIVE guidelines. Figure 3.1.3.2.2 shows the corresponding traffic light plot.

**Figure 3.1.3.2.1**

```{r warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_summary(df, "TvC", "Cognition")
```

**Figure 3.1.3.2.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_traffic(df, "TvC", "Cognition")
```

##### 3.1.4 Outcome 4 : Social interaction

##### 3.1.4.1 Risks of bias

Figure 3.1.4.1.1 shows the risk of bias summary for studies investigating the effect of administering a TAAR1 agonist on social interaction in animals. The risk of bias assessment was performed using the SYRCLE's RoB tool. Figure 3.1.4.1.2 shows the corresponding traffic light plot.

**Figure 3.1.4.1.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_summary(df, "TvC", "Social interaction")
```

**Figure 3.1.4.1.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_traffic(df, "TvC", "Social interaction")
```

##### 3.1.4.2 Reporting quality

Figure 3.1.4.2.1 shows the reporting quality summary for studies investigating the effect of administering a TAAR1 agonist on social interaction in animals. The reporting quality assessment was performed using the ARRIVE guidelines. Figure 3.1.4.2.2 shows the corresponding traffic light plot.

**Figure 3.1.4.2.1**

```{r warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_summary(df, "TvC", "Social interaction")
```

**Figure 3.1.4.2.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_traffic(df, "TvC", "Social interaction")
```

##### 3.1.5 Outcome 5 : Stereotypy

##### 3.1.5.1 Risks of bias

Figure 3.1.5.1.1 shows the risk of bias summary for studies investigating the effect of administering a TAAR1 agonist on stereotypy in animals. The risk of bias assessment was performed using the SYRCLE's RoB tool. Figure 3.1.5.1.2 shows the corresponding traffic light plot.

**Figure 3.1.5.1.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_summary(df, "TvC", "Stereotypy")
```

**Figure 3.1.5.1.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
SyRCLE_RoB_traffic(df, "TvC", "Stereotypy")
```

##### 3.1.5.2 Reporting quality

Figure 3.1.5.2.1 shows the reporting quality summary for studies investigating the effect of administering a TAAR1 agonist on stereotypy in animals. The reporting quality assessment was performed using the ARRIVE guidelines. Figure 3.1.5.2.2 shows the corresponding traffic light plot.

**Figure 3.1.5.2.1**

```{r warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_summary(df, "TvC", "Stereotypy")
```

**Figure 3.1.5.2.2**

```{r warning=FALSE, eval = TRUE, echo = FALSE}
ARRIVE_traffic(df, "TvC", "Stereotypy")
```

# 4. Meta-analyses by experiment type and outcome

Outcomes with ≥2 independent effect sizes were proceeded to meta-analysis. In this iteration of the review, this includes `r df %>% group_by(outcome_type) %>% filter(n_distinct(StudyId) > 1) %>% summarise(n = n_distinct(StudyId)) %>% arrange(desc(n)) %>% pull(outcome_type) %>% unique() %>% tolower() %>% { if (length(.) > 1) paste(paste(head(., -1), collapse = ", "), "and", tail(., 1)) else .}`.

All analyses were conducted allowing for the following hierarchical levels in a random effects model, which accounts for features common to experimental contrasts such as a shared control group:

-   **Level 1: Rodent strain** - effect sizes measured across experiments using the same rodent strain

-   **Level 2: Study** - effect sizes measured from different experiments presented in the same publication

-   **Level 3: Experiment** - effect sizes measured in the same experiment within a study, where often a control group contributes to several effect sizes

*NB: We constructed multilevel models without Knapp-Hartung adjustments as these are not available for rma.mv class objects in the metafor package* ([metafor](https://cran.r-project.org/web/packages/metafor/metafor.pdf)). *Instead, the model is set to `test = "t"` to use t- and F-distributions for making inferences, and `dfs="contain"` to improve the method of approximating degrees of freedom of these distributions.*

The scales/units used to measure outcomes in preclinical studies often differ between studies. The primary effect size used for meta-analysis of preclinical studies is therefore the standardised mean difference (SMD, Hedge's g). We also present a sensitivity analysis using normalised mean difference (NMD) where there are sufficient data for sham proceedures to allow this.

No studies were excluded on the basis of extreme effect sizes reported.

## 4.1 Simple interventions

### 4.1.1 Outcome 1: Locomotor activity (a primary outcome)

The effect of administering a TAAR1 agonist on locomotor activity in animals using SMD as the effect size is shown in Figure 4.1.1. The pooled estimate for SMD across all individual comparisons is displayed as a diamond shape at the bottom of the plot. Dotted lines indicate the prediction interval of the pooled estimate.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA <- run_ML_SMD(df, "TvC", "Locomotor activity", 0.5)
```

**Figure 4.1.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, fig.height=10}
forest_metafor(SMD_S_LMA, "TvC", "Locomotor activity")
```

For simple interventions, TAAR1 interventions had a pooled effect on locomotor activity of SMD = `r SMD_S_LMA[["beta"]]` (95% CI: `r SMD_S_LMA[["ci.lb"]]` to `r SMD_S_LMA[["ci.ub"]]`) with a prediction interval of `r predict(SMD_S_LMA)$pi.lb` to `r predict(SMD_S_LMA)$pi.ub`.

Between-strain variance was `r SMD_S_LMA$sigma2[1]`, between-study variance was `r SMD_S_LMA$sigma2[2]`, and within-study variance (between experiments) was `r SMD_S_LMA$sigma2[3]`

### 4.1.2 Outcome 2: Cognition (a secondary outcome)

The effect of administering a TAAR1 agonist on cognitive outcomes in animals using SMD as the effect size is shown in Figure 4.1.2. The pooled estimate for SMD across all individual comparisons is displayed as a diamond shape at the bottom of the plot. Dotted lines indicate the prediction interval of the pooled estimate.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog <- run_ML_SMD(df, "TvC", "Cognition", 0.5)
```

**Figure 4.1.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, fig.height=7}
forest_metafor(SMD_S_cog, "TvC", "cognition")
```

For simple interventions, TAAR1 interventions had a pooled effect on cognitive outcomes of SMD = `r SMD_S_cog[["beta"]]` (95% CI: `r SMD_S_cog[["ci.lb"]]` to `r SMD_S_cog[["ci.ub"]]`) with a prediction interval of `r predict(SMD_S_cog)$pi.lb` to `r predict(SMD_S_cog)$pi.ub`.

Between-strain variance was `r SMD_S_cog$sigma2[1]`, between-study variance was `r SMD_S_cog$sigma2[2]`, and within-study variance (between experiments) was `r SMD_S_cog$sigma2[3]`

## 4.2 "Head to head" (TAAR1 Ag v known antipsychotic drugs) experiments

### 4.2.1 Outcome 1: Locomotor activity (a primary outcome)

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_H2H <- run_ML_SMD(df, "TvA", "Locomotor activity", 0.5)
```

For head to head comparisons, TAAR1 interventions had a pooled effect on locomotor activity of SMD = `r SMD_S_LMA_H2H[["beta"]]` (95% CI: `r SMD_S_LMA_H2H[["ci.lb"]]` to `r SMD_S_LMA_H2H[["ci.ub"]]` with a prediction interval of `r predict(SMD_S_LMA_H2H)$pi.lb` to `r predict(SMD_S_LMA_H2H)$pi.ub`.

Between-strain variance was `r SMD_S_LMA_H2H$sigma2[1]`, between-study variance was `r SMD_S_LMA_H2H$sigma2[2]`, and within-study variance (between experiments) was `r SMD_S_LMA_H2H$sigma2[3]`

**Figure 4.2.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, fig.height=10}
forest_metafor(SMD_S_LMA_H2H, "TvA", "locomotor activity")
```

For these analyses, the use of VCV Matrix in multilevel regression leads to very wide confidence intervals and prediction intervals.

### 4.2.2 Outcome 2: Cognition (a secondary outcome)

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_Cog_H2H <- run_ML_SMD(df, "TvA", "Cognition", 0.5)
```

For head to head comparisons, TAAR1 interventions had a pooled effect on cognitive outcomes of SMD = `r SMD_S_Cog_H2H[["beta"]]` (95% CI: `r SMD_S_Cog_H2H[["ci.lb"]]` to `r SMD_S_Cog_H2H[["ci.ub"]]` with a prediction interval of `r predict(SMD_S_Cog_H2H)$pi.lb` to `r predict(SMD_S_Cog_H2H)$pi.ub`.

Between-strain variance was `r SMD_S_Cog_H2H$sigma2[1]`, between-study variance was `r SMD_S_Cog_H2H$sigma2[2]`, and within-study variance (between experiments) was `r SMD_S_Cog_H2H$sigma2[3]`

**Figure 4.2.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, fig.height=10}
forest_metafor(SMD_S_Cog_H2H, "TvA","Cognition")
```

# 4.3 "Positive control" (known antipsychotic drug v control) experiments

### 4.3.1 Outcome 1: Locomotor activity (a primary outcome)

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_PC <- run_ML_SMD(df, "AvC", "Locomotor activity", 0.5)
```

**Figure 4.3.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, fig.height=10}
forest_metafor(SMD_S_LMA_PC, "AvC","Locomotor activity")
```

For positive control experiments, known antipsychotic drugs had a pooled effect on locomotor activity of SMD = `r SMD_S_LMA_PC[["beta"]]` (95% CI: `r SMD_S_LMA_PC[["ci.lb"]]` to `r SMD_S_LMA_PC[["ci.ub"]]` with a prediction interval of `r predict(SMD_S_LMA_PC)$pi.lb` to `r predict(SMD_S_LMA_PC)$pi.ub`.

Between-strain variance was `r SMD_S_LMA_PC$sigma2[1]`, between-study variance was `r SMD_S_LMA_PC$sigma2[2]`, and within-study variance (between experiments) was `r SMD_S_LMA_PC$sigma2[3]`

### 4.3.2 Outcome 2: Cognition (a secondary outcome)

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_Cog_PC <- run_ML_SMD(df, "AvC", "Cognition", 0.5)
```

**Figure 4.3.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, fig.height=10}
forest_metafor(SMD_S_Cog_PC, "AvC","Cognition")
```

For positive control experiments, known antipsychotic drugs had a pooled effect on cognitive outcomes of SMD = `r SMD_S_Cog_PC[["beta"]]` (95% CI: `r SMD_S_Cog_PC[["ci.lb"]]` to `r SMD_S_Cog_PC[["ci.ub"]]` with a prediction interval of `r predict(SMD_S_Cog_PC)$pi.lb` to `r predict(SMD_S_Cog_PC)$pi.ub`.

Between-strain variance was `r SMD_S_Cog_PC$sigma2[1]`, between-study variance was `r SMD_S_Cog_PC$sigma2[2]`, and within-study variance (between experiments) was `r SMD_S_Cog_PC$sigma2[3]`

# 4.4 Combination treatment (TAAR1 Agonist plus conventional antipsychotic v conventional antipsychotic alone)

### 4.4.1 Outcome 1: Locomotor activity (a primary outcome)

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_TAA <- run_ML_SMD(df, "TAvA", "Locomotor activity", 0.5)
```

**Figure 4.4.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, fig.height=10}
forest_metafor(SMD_S_LMA_TAA, "TAvA","Locomotor activity")
```

For positive control experiments, known antipsychotic drugs had a pooled effect on locomotor activity of SMD = `r SMD_S_LMA_TAA[["beta"]]` (95% CI: `r SMD_S_LMA_TAA[["ci.lb"]]` to `r SMD_S_LMA_TAA[["ci.ub"]]` with a prediction interval of `r predict(SMD_S_LMA_TAA)$pi.lb` to `r predict(SMD_S_LMA_TAA)$pi.ub`.

Between-strain variance was `r SMD_S_LMA_TAA$sigma2[1]`, between-study variance was `r SMD_S_LMA_TAA$sigma2[2]`, and within-study variance (between experiments) was `r SMD_S_LMA_TAA$sigma2[3]`

### 4.4.2 Outcome 2: Cognition (a secondary outcome)

No such studies were identified

# 5. Metaregression

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
options(scipen=100, digits=3)
```

For each outcome, the covariates of interest for subgroup analyses were:

-   **Sex**

-   **Category of disease induction**

-   **Route of intervention administration** <!--# is this method of induction in the protocol? -->

-   **Whether the intervention was prophylactic or therapeutic (i.e. administered before or after disease model induction)** <!--#  is this also method of induction? -->

-   **Duration of treatment period**

-   **The intervention administered** <!--# where is this in the protocol? -->

-   **The efficacy of the drug (i.e. whether the drug is a partial or full agonist)**

-   **The selectivity of the drug**

-   **Potency of the intervention**

-   **Dose of intervention**

We also conducted subgroup analyses using **(1) SYRCLE Risk of Bias** and **(2) ARRIVE reporting quality** assessment scores as covariates to evaluate their influence on effect size estimates. These were not specified in the study protocol, but evaluation of risk of bias is required for the Sammary of Evidence table, and no studies were considered at low risk of bias or high reporting quality to allow such a sensitivity analysis

## 5.1 Simple interventions

### 5.1.1 Outcome 1: Locomotor activity

##### 5.1.1.1 Sex

Figure 5.1.1.1 displays the estimates for the pooled SMD's when comparisons are stratified by sex of the animal. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by sex, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=8.5, fig.height=3}
SMD_S_LMA_sex <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "Sex", 0.5)
```

`r SMD_S_LMA_sex$subgroup_rma_summary[SMD_S_LMA_sex$subgroup_rma_summary$Sex == "Not reported", "k"]` comparisons did not report the sex of the animals used within the experimental cohort. `r SMD_S_LMA_sex$subgroup_rma_summary[SMD_S_LMA_sex$subgroup_rma_summary$Sex == "Male", "k"]` comparisons used cohorts of only male animals and `r SMD_S_LMA_sex$subgroup_rma_summary[SMD_S_LMA_sex$subgroup_rma_summary$Sex == "Female", "k"]` comparisons used cohorts of only female animals. There were `r SMD_S_LMA_sex$subgroup_rma_summary[SMD_S_LMA_sex$subgroup_rma_summary$Sex == "Mixed male and female", "k"]` comparisons using cohorts of both male and female animals.

The pooled SMD estimate for male animals was `r SMD_S_LMA_sex$subgroup_rma_summary[SMD_S_LMA_sex$subgroup_rma_summary$Sex == "Male", "SMD"]`, for females `r SMD_S_LMA_sex$subgroup_rma_summary[SMD_S_LMA_sex$subgroup_rma_summary$Sex == "Female", "SMD"]`, and for mixed cohorts `r SMD_S_LMA_sex$subgroup_rma_summary[SMD_S_LMA_sex$subgroup_rma_summary$Sex == "Mixed male and female", "SMD"]`. The pooled SMD estimate for comparisons not reporting the sex of the animals within the experimental cohort was `r SMD_S_LMA_sex$subgroup_rma_summary[SMD_S_LMA_sex$subgroup_rma_summary$Sex == "Not reported", "SMD"]`.

##### 5.1.1.2 Category of disease induction

Figure 5.1.1.2 displays the estimates for the pooled SMD's when comparisons are stratified by the category of disease induction. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by category of disease induction, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=11, fig.height=2.5}
SMD_S_LMA_CatDisInd <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "CategoryDiseaseInduction", 0.5)
```

`r SMD_S_LMA_CatDisInd$subgroup_rma_summary[SMD_S_LMA_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Pharmacological (e.g. psychostimulants, NMDA antagonists)", "k"]` comparisons used pharmacological methods to induce the disease model. `r SMD_S_LMA_CatDisInd$subgroup_rma_summary[SMD_S_LMA_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Genetic (e.g. DISC1 KO, DAT KO, D2R overexpression)", "k"]` comparisons used genetic methods to induce the disease model.

The pooled SMD estimate for comparisons using pharmacological methods to induce the disease model was `r SMD_S_LMA_CatDisInd$subgroup_rma_summary[SMD_S_LMA_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Pharmacological (e.g. psychostimulants, NMDA antagonists)", "SMD"]`, and for comparisons using genetic methods to induce the disease model `r SMD_S_LMA_CatDisInd$subgroup_rma_summary[SMD_S_LMA_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Genetic (e.g. DISC1 KO, DAT KO, D2R overexpression)", "SMD"]`.

##### 5.1.1.3 Route of intervention administration

Figure 5.1.1.3 displays the estimates for the pooled SMD's when comparisons are stratified by the route of intervention administration. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by route of intervention administration, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.3**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=2}
SMD_S_LMA_AdminRoute <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "InterventionAdministrationRoute", 0.5)
```

`r SMD_S_LMA_AdminRoute$subgroup_rma_summary[SMD_S_LMA_AdminRoute$subgroup_rma_summary$InterventionAdministrationRoute == "Intraperitoneal (IP) injection", "k"]` comparisons administered the TAAR1 agonist intraperitoneally. `r SMD_S_LMA_AdminRoute$subgroup_rma_summary[SMD_S_LMA_AdminRoute$subgroup_rma_summary$InterventionAdministrationRoute == "Oral administration/gavage", "k"]` comparisons administered the TAAR1 agonist orally.

The pooled SMD estimate for experiments administering the TAAR1 agonist intraperitoneally was `r SMD_S_LMA_AdminRoute$subgroup_rma_summary[SMD_S_LMA_AdminRoute$subgroup_rma_summary$InterventionAdministrationRoute == "Intraperitoneal (IP) injection", "SMD"]`, and for experiments administering the TAAR1 agonist orally `r SMD_S_LMA_AdminRoute$subgroup_rma_summary[SMD_S_LMA_AdminRoute$subgroup_rma_summary$InterventionAdministrationRoute == "Oral administration/gavage", "SMD"]`.

##### 5.1.1.4 Prophylactic or therapeutic intervention

Figure 5.1.1.4 displays the estimates for the pooled SMD's when comparisons are stratified by whether the intervention was administered prophylactically or therapeutically. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by whether the intervention was administered prophylactically or therapeutically, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.4**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=3}
SMD_S_LMA_ProphThera <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "ProphylacticOrTherapeutic", 0.5)
```

`r SMD_S_LMA_ProphThera$subgroup_rma_summary[SMD_S_LMA_ProphThera$subgroup_rma_summary$ProphylacticOrTherapeutic == "Prophylactic", "k"]` comparisons administered the TAAR1 agonist prophylactically. `r SMD_S_LMA_ProphThera$subgroup_rma_summary[SMD_S_LMA_ProphThera$subgroup_rma_summary$ProphylacticOrTherapeutic == "Therapeutic", "k"]` comparisons administered the TAAR1 agonist therapeutically.

The pooled SMD estimate for experiments administering the TAAR1 agonist prophylactically was `r SMD_S_LMA_ProphThera$subgroup_rma_summary[SMD_S_LMA_ProphThera$subgroup_rma_summary$ProphylacticOrTherapeutic == "Prophylactic", "SMD"]`, and for experiments administering the TAAR1 agonist therapeutically `r SMD_S_LMA_ProphThera$subgroup_rma_summary[SMD_S_LMA_ProphThera$subgroup_rma_summary$ProphylacticOrTherapeutic == "Therapeutic", "SMD"]`.

##### 5.1.1.5 Duration of treatment period

In this iteration of the review, all relevant comparisons administered the TAAR1 agonist for \< 1 week. Therefore, no subgroup analyses were conducted for this variable.

##### 5.1.1.6 The intervention administered

Figure 5.1.1.6 displays the estimates for the pooled SMD's when comparisons are stratified by the intervention administered. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by the intervention administered, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.6**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_LMA_Drug <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "DrugName", 0.5)
```

The TAAR1 agonist SEP-363856 (Ultaront) was administered in `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "SEP-363856", "k"]` experiments. `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5203648", "k"]` experiments used the TAAR1 agonist RO5203648, `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5166017", "k"]` used RO5166017, `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5263397", "k"]` used RO5263397, `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5256390", "k"]` used RO5256390, `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5073012", "k"]` used RO5073012. `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "LK000764", "k"]` experiments used the TAAR1 agonist LK000764 and `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "AP163", "k"]` used AP163. `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "Compound 50A", "k"]` experiments assessed the effect of the TAAR1 agonist Compound 50A and `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "Compound 50B", "k"]` experiments assessed that of Compound 50B. Note that Compound 50A and 50B were specific to one study, and chemical registry identifiers were neither provided or able to be found.

The pooled SMD estimate for experiments administering the TAAR1 agonist SEP-363856 was `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "SEP-363856", "SMD"]`. For experiments administering the TAAR1 agonist RO5203648 the pooled estimate was `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5203648", "SMD"]`. For experiments administering the TAAR1 agonist RO5166017 `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5166017", "SMD"]`, for experiments administering the TAAR1 agonist RO5263397 `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5263397", "SMD"]`, for experiments administering the TAAR1 agonist RO5256390 `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5256390", "SMD"]`, for experiments administering the TAAR1 agonist RO5073012 `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "RO5073012", "SMD"]`, for experiments administering the TAAR1 agonist LK000764 `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "LK000764", "SMD"]`, for experiments administering the TAAR1 agonist AP163 `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "AP163", "SMD"]`, for experiments administering the TAAR1 agonist Compound 50A `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "Compound 50A", "SMD"]`, and for experiments administering the TAAR1 agonist Compound 50B `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "Compound 50B", "SMD"]`.

##### 5.1.1.7 The efficacy of the drug (i.e. whether the drug is a partial or full agonist)

Figure 5.1.1.7 displays the estimates for the pooled SMD's when comparisons are stratified by the action/efficacy of the intervention administered. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by intervention efficacy, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.7**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_LMA_DrugEfficacy <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "Efficacy", 0.5)
```

TAAR1 partial agonists were used in `r SMD_S_LMA_DrugEfficacy$subgroup_rma_summary[SMD_S_LMA_DrugEfficacy$subgroup_rma_summary$Efficacy == "TAAR1 partial agonist", "k"]` experiments. TAAR1 full agonists were used in `r SMD_S_LMA_DrugEfficacy$subgroup_rma_summary[SMD_S_LMA_DrugEfficacy$subgroup_rma_summary$Efficacy == "TAAR1 full agonist", "k"]` experiments.

The pooled SMD estimate for experiments administering a TAAR1 partial agonist was `r SMD_S_LMA_DrugEfficacy$subgroup_rma_summary[SMD_S_LMA_DrugEfficacy$subgroup_rma_summary$Efficacy == "TAAR1 partial agonist", "SMD"]` and for those administering a TAAR1 full agonist `r SMD_S_LMA_DrugEfficacy$subgroup_rma_summary[SMD_S_LMA_DrugEfficacy$subgroup_rma_summary$Efficacy == "TAAR1 full agonist", "SMD"]`.

##### 5.1.1.8 The selectivity of the drug

Figure 5.1.1.8 displays the estimates for the pooled SMD's when comparisons are stratified by the selectivity of the intervention administered. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by intervention selectivity, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.8**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_LMA_DrugSelectivity <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "Selectivity", 0.5)
```

TAAR1 agonists with high selectivity were used in `r SMD_S_LMA_DrugSelectivity$subgroup_rma_summary[SMD_S_LMA_DrugSelectivity$subgroup_rma_summary$Selectivity == "High", "k"]` experiments. TAAR1 drugs with additional agonist activity at serotonin 5HT1A receptors were used in `r SMD_S_LMA_DrugSelectivity$subgroup_rma_summary[SMD_S_LMA_DrugEfficacy$subgroup_rma_summary$Selectivity == "Low (5HT1A partial agonism)", "k"]` experiments. The selectivity of the TAAR1 agonist used in `r SMD_S_LMA_DrugSelectivity$subgroup_rma_summary[SMD_S_LMA_DrugEfficacy$subgroup_rma_summary$Selectivity == "Unclear", "k"]` experiments was unclear/remains undetermined.

The pooled SMD estimate for experiments administering a TAAR1 agonist with high selectivity was `r SMD_S_LMA_DrugSelectivity$subgroup_rma_summary[SMD_S_LMA_DrugSelectivity$subgroup_rma_summary$Selectivity == "High", "SMD"]`. The estimate for experiments administering a TAAR1 agonist with low selectivity was `r SMD_S_LMA_DrugSelectivity$subgroup_rma_summary[SMD_S_LMA_DrugSelectivity$subgroup_rma_summary$Selectivity == "Low (5HT1A partial agonism)", "SMD"]`, and for those experiments administering a TAAR1 agonist with an unknown selectivity `r SMD_S_LMA_DrugSelectivity$subgroup_rma_summary[SMD_S_LMA_DrugSelectivity$subgroup_rma_summary$Selectivity == "Unclear", "SMD"]`.

#### 5.1.1.9 Potency of intervention

The pEC50 value of each drug was used to measure potency. The pEC50 value is the negative logarithm (to base 10) of the EC50 value. Higher pEC50 values indicate higher potency (as they indicate a lower EC50). Figure x displays a visualisation of the meta-regression using the pEC50 value as an explanatory variable. Dashed lines represent the 95% confidence interval of the regression line. The dotted lines represent the 95% prediction interval. Raw data is plotted with 'bubble' size adjusted according to effect size precision.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_potency <- metaregression_analysis(df, "TvC", "Locomotor activity", "pE50", 0.5)
```

**Figure 5.1.1.9**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_potency$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_potency$metaregression_summary$beta[1]`. This gives the predicted SMD when the pEC50 of the intervention is 0. Note that this should be interpreted with caution; since the logarithm of zero is undefined (it tends towards negative infinity), a pEC50 value cannot be 0 unless the EC50 is 1 mol/L. The estimate for $\theta$ can be interpreted as the estimated SMD when the EC50 is 1 mol/L (1000mM), which signifies extremely low potency.

The estimate for $\beta$ was `r SMD_S_LMA_potency$metaregression_summary$beta[2]`. This represents the predicted regression weight for the pEC50 of the intervention.

#### 5.1.1.10 Dose of intervention

In this iteration of the review, the TAAR1 agonists administered in 'simple intervention' experiments (ordered by number of experiments) were; **`r drugs <- df %>% filter(SortLabel == "TvC") %>% filter(outcome_type == "Locomotor activity") %>% group_by(DrugName) %>% summarise(count = n()) %>% arrange(desc(count)) %>% pull(DrugName); if (length(drugs) > 1) {paste(paste(head(drugs, -1), collapse = ", "), "and", tail(drugs, 1))} else {drugs}`**. Meta-regression using the administered dose as an explanatory variable was first conducted individually for each drug/intervention. This approach accounts for varying mechanisms of action, pharmacodynamics, and pharmacokinetics of each drug, ensuring that the dose effect of one intervention is not masked by aggregate data.

In the following plots, dashed lines represent the 95% confidence interval of the regression line and dotted lines represent the 95% prediction interval. Raw data is plotted with point size adjusted according to effect size precision.

##### 5.1.1.10.1 SEP-363856 (Ultaront)

Figure 5.1.1.10.1 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of SEP-363856 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_SEP363856_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "SEP-363856", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_SEP363856_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_SEP363856_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_SEP363856_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.2 RO5203648

Figure 5.1.1.10.2 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of RO5203648 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_RO5203648_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "RO5203648", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_RO5203648_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_RO5203648_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_RO5203648_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.3 RO5166017

Figure 5.1.1.10.3 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of RO5166017 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_RO5166017_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "RO5166017", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.3**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_RO5166017_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_RO5166017_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_RO5166017_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.4 RO5263397

Figure 5.1.1.10.4 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of RO5263397 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_RO5263397_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "RO5263397", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.4**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_RO5263397_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_RO5263397_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_RO5263397_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.5 RO5256390

Figure 5.1.1.10.5 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of RO5256390 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_RO5256390_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "RO5256390", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.5**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_RO5256390_dose$regression_plot
```

##### 5.1.1.10.6 LK000764

Figure 5.1.1.10.6 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of LK000764 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_LK000764_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "LK000764", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.6**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_LK000764_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_LK000764_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_LK000764_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.7 Compound 50B

Figure 5.1.1.10.7 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of Compound 50B (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_Compound50B_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "Compound 50B", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.7**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_Compound50B_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_Compound50B_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_Compound50B_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.8 Compound 50A

Figure 5.1.1.10.8 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of Compound 50A (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_Compound50A_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "Compound 50A", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.8**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_Compound50A_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_Compound50A_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_Compound50A_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.9 RO5073012

Figure 5.1.1.10.9 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of RO5073012 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_RO5073012_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "RO5073012", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.9**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_RO5073012_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_RO5073012_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_RO5073012_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.10 AP163

Figure 5.1.1.10.10 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying doses of AP163 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_AP163_dose <- metaregression_analysis_by_drug(df, "TvC", "Locomotor activity", "AP163", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.1.10.10**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_AP163_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_AP163_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_AP163_dose$metaregression_summary$beta[2]`.

##### 5.1.1.10.11 Standardised dose

We then sought evidence of a dose response relationship across all drugs. To do this, we conducted meta-regression using a standardised dose variable. This variable quantifies the administered dose as a multiple of the drug's EC50, indicating how many times the dose administered was greater (or lesser) than the concentration needed to achieve half-maximal effect. For example, if a drug's dose is twice its EC50, the standardized dose would be 2, indicating that the dose is twice the concentration needed to achieve half-maximal effect.

The standardised dose was calculated by dividing the log-transformed dose of the intervention (in mg/kg) by the product of the intervention's EC50 (in moles) and the Molar mass of the drug (in mg/mol):

$$
\frac{\log(\text{Dose of Intervention (mg/kg)})}{(\text{Molar Mass (g/mol)} \times 1000) \times (\frac{\text{EC50 (micromoles)}}{1000000})}
$$

**This is a simplified approximation based on the reasoning that if drug actions are mediated through the TAAR1 receptor, and drug efficacy is reflected in the respective EC50 values, then theoretically drugs should exhibit similar effects when acting at their respective EC50.**

The actual concentration of a drug at the receptor site is influenced by several variables, including dosage, administration route, elimination half-life, and first-pass metabolism (in case of oral administration). Incorporating all these factors accurately would necessitate a detailed pharmacokinetic model, which falls outside the scope of this review. Consequently, we assume uniformity across experiments in terms of (i) volume of distribution, (ii) first-pass metabolism, (iii) blood-brain barrier permeability, and (iv) experimental design, especially regarding the timing of peak drug concentration (where we assume that experiments were designed to be done at a time when the drug was near peak concentration).

Figure x provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in locomotor activity to varying standardised doses of TAAR1 agonists. As before, dashed lines represent the 95% confidence interval of the regression line and dotted lines represent the 95% prediction interval. Raw data is plotted with point size adjusted according to effect size precision.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_StandardDose <- metaregression_analysis(df, "TvC", "Locomotor activity", "StandardisedDose", 0.5)
```

**Figure 5.1.1.10.11**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_LMA_StandardDose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_LMA_StandardDose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_LMA_StandardDose$metaregression_summary$beta[2]`.

##### 5.1.1.11 SYRCLE RoB assessment

Figure 5.1.2.11 displays the estimates for the pooled SMD's when comparisons are stratified by how many of the SYRCLE risk of bias assessment criteria (of which there are 10) that the experiment met. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by SYRCLE Risk of Bias, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.11**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_LMA_SYRCLERoB <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "RoBScore", 0.5)
```

`r SMD_S_LMA_SYRCLERoB$subgroup_rma_summary[SMD_S_LMA_SYRCLERoB$subgroup_rma_summary$RoBScore == "0 criteria met", "k"]` experiments met none of the SYRCLE Risk of Bias criteria. `r SMD_S_LMA_SYRCLERoB$subgroup_rma_summary[SMD_S_LMA_SYRCLERoB$subgroup_rma_summary$RoBScore == "1 criteria met", "k"]` experiments met one of the SYRCLE Risk of Bias criteria. `r SMD_S_LMA_SYRCLERoB$subgroup_rma_summary[SMD_S_LMA_SYRCLERoB$subgroup_rma_summary$RoBScore == "2 criteria met", "k"]` experiments met two of the SYRCLE Risk of Bias criteria. No experiments met more than two of the SYRCLE Risk of Bias criteria.

The pooled SMD estimate for the effect of TAAR1 agonists on locomotor activity in experiments that met none of the SYRCLE Risk of Bias criteria was `r SMD_S_LMA_SYRCLERoB$subgroup_rma_summary[SMD_S_LMA_SYRCLERoB$subgroup_rma_summary$RoBScore == "0 criteria met", "SMD"]`. The estimate for experiments that met one of the SYRCLE Risk of Bias criteria was `r SMD_S_LMA_SYRCLERoB$subgroup_rma_summary[SMD_S_LMA_SYRCLERoB$subgroup_rma_summary$RoBScore == "1 criteria met", "SMD"]`, and for those experiments that met two of the SYRCLE Risk of Bias criteria `r SMD_S_LMA_SYRCLERoB$subgroup_rma_summary[SMD_S_LMA_SYRCLERoB$subgroup_rma_summary$RoBScore == "2 criteria met", "SMD"]`.

Figure 5.1.1.11 displays the estimates for the pooled SMD's when comparisons are stratified by this categorisation that the experiment met. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by SyRCLE Risk of Bias score, is displayed as a diamond shape at the bottom of the plot.

##### 5.1.1.12 ARRIVE reporting quality guidelines

Experiments were categorised based on the number of ARRIVE guidelines (of which there are 23) met. The categorisation was as follows: Experiments meeting 3 or fewer criteria were labeled as "A: \< 3 criteria met"; those meeting 4 to 7 criteria were labeled "B: 4-7 criteria met"; for 8 to 11 criteria, "C: 8-11 criteria met"; for 12 to 15 criteria, "D: 12-15 criteria met"; for 16 to 19 criteria, "E: 16-19 criteria met"; and experiments meeting more than 19 criteria were labeled as "F: \> 20 criteria met".

Figure 5.1.1.12 displays the estimates for the pooled SMD's when comparisons are stratified by this categorisation that the experiment met. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by ARRIVE reporting quality guidelines, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.1.12**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_LMA_ARRIVE <- plot_subgroup_analysis(df, "TvC", "Locomotor activity", "ARRIVEScoreCat", 0.5)
```

`r SMD_S_LMA_ARRIVE$subgroup_rma_summary[SMD_S_LMA_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "B: 4-7 criteria met", "k"]` experiments met between 4-7 of the ARRIVE reporting quality criteria. `r SMD_S_LMA_ARRIVE$subgroup_rma_summary[SMD_S_LMA_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "C: 8-11 criteria met", "k"]` experiments met between 8-11, `r SMD_S_LMA_ARRIVE$subgroup_rma_summary[SMD_S_LMA_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "D: 12-15 criteria met", "k"]` experiments met between 12-15, `r SMD_S_LMA_ARRIVE$subgroup_rma_summary[SMD_S_LMA_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "E: 16-19 criteria met", "k"]` experiments met between 16-19. No experiment met below 4 or above 19 of the ARRIVE reporting quality criteria.

The pooled SMD estimate for the effect of TAAR1 agonists on locomotor activity in experiments that met between 4-7 of the ARRIVE reporting quality criteria was `r SMD_S_LMA_ARRIVE$subgroup_rma_summary[SMD_S_LMA_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "4-7 criteria met", "SMD"]`. The estimate for experiments that met between 8-11 of the ARRIVE reporting quality criteria was `r SMD_S_LMA_ARRIVE$subgroup_rma_summary[SMD_S_LMA_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "8-11 criteria met", "SMD"]`, for those experiments that met between 12-15 of the ARRIVE reporting quality criteria `r SMD_S_LMA_ARRIVE$subgroup_rma_summary[SMD_S_LMA_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "12-15 criteria met", "SMD"]`, and for those experiments that met between 16-19 of the ARRIVE reporting quality criteria `r SMD_S_LMA_ARRIVE$subgroup_rma_summary[SMD_S_LMA_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "16-19 criteria met", "SMD"]`.

##### 5.1.1.13 Heterogeneity explained by covariates (simple interventions on locomotor activity)

The table below shows which of the covariates, if any, explain some of the heterogeneity observed in the effect sizes of the effect of TAAR1 agonists on locomotor activity. We present marginal R^2^, which measures the proportion of variance explained by including moderators in the model.

|                Moderator                 |        Category         |                         $\beta$                         |                                                       95% CI                                                        |                       Marginal R^2^                       |
|:-------------:|:-------------:|:-------------:|:-------------:|:-------------:|
|              Overall effect              |           \-            |                  `r SMD_S_LMA$beta[1]`                  |                                      `r SMD_S_LMA$ci.lb` - `r SMD_S_LMA$ci.ub`                                      |                            \-                             |
|                   Sex                    |           \-            |                           \-                            |                                                         \-                                                          |       `r r2_ml(SMD_S_LMA_sex$subgroup_analysis)[1]`       |
|                    \-                    |        *Female*         |       `r SMD_S_LMA_sex$subgroup_analysis$beta[1]`       |             `r SMD_S_LMA_sex$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_sex$subgroup_analysis$ci.ub[1]`             |                            \-                             |
|                    \-                    |         *Male*          |       `r SMD_S_LMA_sex$subgroup_analysis$beta[2]`       |             `r SMD_S_LMA_sex$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_sex$subgroup_analysis$ci.ub[2]`             |                            \-                             |
|                    \-                    |         *Mixed*         |       `r SMD_S_LMA_sex$subgroup_analysis$beta[3]`       |             `r SMD_S_LMA_sex$subgroup_analysis$ci.lb[3]` - `r SMD_S_LMA_sex$subgroup_analysis$ci.ub[3]`             |                            \-                             |
|                    \-                    |     *Not reported*      |       `r SMD_S_LMA_sex$subgroup_analysis$beta[4]`       |             `r SMD_S_LMA_sex$subgroup_analysis$ci.lb[4]` - `r SMD_S_LMA_sex$subgroup_analysis$ci.ub[4]`             |                            \-                             |
|   Category of disease model induction    |           \-            |                           \-                            |                                                         \-                                                          |    `r r2_ml(SMD_S_LMA_CatDisInd$subgroup_analysis)[1]`    |
|                    \-                    |        *Genetic*        |    `r SMD_S_LMA_CatDisInd$subgroup_analysis$beta[1]`    |       `r SMD_S_LMA_CatDisInd$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_CatDisInd$subgroup_analysis$ci.ub[1]`       |                            \-                             |
|                    \-                    |    *Pharmacological*    |    `r SMD_S_LMA_CatDisInd$subgroup_analysis$beta[2]`    |       `r SMD_S_LMA_CatDisInd$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_CatDisInd$subgroup_analysis$ci.ub[2]`       |                            \-                             |
|           Administration route           |           \-            |                           \-                            |                                                         \-                                                          |   `r r2_ml(SMD_S_LMA_AdminRoute$subgroup_analysis)[1]`    |
|                    \-                    |    *Intraperitoneal*    |   `r SMD_S_LMA_AdminRoute$subgroup_analysis$beta[1]`    |      `r SMD_S_LMA_AdminRoute$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_AdminRoute$subgroup_analysis$ci.ub[1]`      |                            \-                             |
|                    \-                    |         *Oral*          |   `r SMD_S_LMA_AdminRoute$subgroup_analysis$beta[2]`    |      `r SMD_S_LMA_AdminRoute$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_AdminRoute$subgroup_analysis$ci.ub[2]`      |                            \-                             |
| Prophylactic or therapeutic intervention |           \-            |                           \-                            |                                                         \-                                                          |   `r r2_ml(SMD_S_LMA_ProphThera$subgroup_analysis)[1]`    |
|                    \-                    |     *Prophylactic*      |   `r SMD_S_LMA_ProphThera$subgroup_analysis$beta[1]`    |      `r SMD_S_LMA_ProphThera$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_ProphThera$subgroup_analysis$ci.ub[1]`      |                            \-                             |
|                    \-                    |      *Therapeutic*      |   `r SMD_S_LMA_ProphThera$subgroup_analysis$beta[2]`    |      `r SMD_S_LMA_ProphThera$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_ProphThera$subgroup_analysis$ci.ub[2]`      |                            \-                             |
|        Intervention administered         |           \-            |                           \-                            |                                                         \-                                                          |      `r r2_ml(SMD_S_LMA_Drug$subgroup_analysis)[1]`       |
|                    \-                    |         *AP163*         |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[1]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[1]`            |                            \-                             |
|                    \-                    |     *Compound 50A*      |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[2]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[2]`            |                            \-                             |
|                    \-                    |     *Compound 50B*      |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[3]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[3]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[3]`            |                            \-                             |
|                    \-                    |       *LK000764*        |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[4]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[4]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[4]`            |                            \-                             |
|                    \-                    |       *RO5073012*       |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[5]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[5]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[5]`            |                            \-                             |
|                    \-                    |       *RO5166017*       |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[6]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[6]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[6]`            |                            \-                             |
|                    \-                    |       *RO5203648*       |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[7]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[7]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[7]`            |                            \-                             |
|                    \-                    |       *RO5256390*       |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[8]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[8]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[8]`            |                            \-                             |
|                    \-                    |       *RO5263397*       |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[9]`       |            `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[9]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[9]`            |                            \-                             |
|                    \-                    | *SEP-363856 (Ultaront)* |      `r SMD_S_LMA_Drug$subgroup_analysis$beta[10]`      |           `r SMD_S_LMA_Drug$subgroup_analysis$ci.lb[10]` - `r SMD_S_LMA_Drug$subgroup_analysis$ci.ub[10]`           |                            \-                             |
|              Drug efficacy               |           \-            |                           \-                            |                                                         \-                                                          |  `r r2_ml(SMD_S_LMA_DrugEfficacy$subgroup_analysis)[1]`   |
|                    \-                    |     *Full agonist*      |  `r SMD_S_LMA_DrugEfficacy$subgroup_analysis$beta[1]`   |    `r SMD_S_LMA_DrugEfficacy$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_DrugEfficacy$subgroup_analysis$ci.ub[1]`    |                            \-                             |
|                    \-                    |    *Partial agonist*    |  `r SMD_S_LMA_DrugEfficacy$subgroup_analysis$beta[2]`   |    `r SMD_S_LMA_DrugEfficacy$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_DrugEfficacy$subgroup_analysis$ci.ub[2]`    |                            \-                             |
|             Drug selectivity             |           \-            |                           \-                            |                                                         \-                                                          | `r r2_ml(SMD_S_LMA_DrugSelectivity$subgroup_analysis)[1]` |
|                    \-                    |         *High*          | `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$beta[1]` | `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$ci.ub[1]` |                            \-                             |
|                    \-                    |          *Low*          | `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$beta[2]` | `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$ci.ub[2]` |                            \-                             |
|                    \-                    |        *Unclear*        | `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$beta[3]` | `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$ci.lb[3]` - `r SMD_S_LMA_DrugSelectivity$subgroup_analysis$ci.ub[3]` |                            \-                             |
|               Risk of Bias               |           \-            |                           \-                            |                                                         \-                                                          |    `r r2_ml(SMD_S_LMA_SYRCLERoB$subgroup_analysis)[1]`    |
|                    \-                    |    *0 criteria met*     |    `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$beta[1]`    |       `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$ci.ub[1]`       |                            \-                             |
|                    \-                    |    *1 criteria met*     |    `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$beta[2]`    |       `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$ci.ub[2]`       |                            \-                             |
|                    \-                    |    *2 criteria met*     |    `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$beta[3]`    |       `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$ci.lb[3]` - `r SMD_S_LMA_SYRCLERoB$subgroup_analysis$ci.ub[3]`       |                            \-                             |
|            Reporting quality             |           \-            |                           \-                            |                                                         \-                                                          |     `r r2_ml(SMD_S_LMA_ARRIVE$subgroup_analysis)[1]`      |
|                    \-                    |   *4-7 criteria met*    |     `r SMD_S_LMA_ARRIVE$subgroup_analysis$beta[1]`      |          `r SMD_S_LMA_ARRIVE$subgroup_analysis$ci.lb[1]` - `r SMD_S_LMA_ARRIVE$subgroup_analysis$ci.ub[1]`          |                            \-                             |
|                    \-                    |   *8-11 criteria met*   |     `r SMD_S_LMA_ARRIVE$subgroup_analysis$beta[2]`      |          `r SMD_S_LMA_ARRIVE$subgroup_analysis$ci.lb[2]` - `r SMD_S_LMA_ARRIVE$subgroup_analysis$ci.ub[2]`          |                            \-                             |
|                    \-                    |  *12-15 criteria met*   |     `r SMD_S_LMA_ARRIVE$subgroup_analysis$beta[3]`      |          `r SMD_S_LMA_ARRIVE$subgroup_analysis$ci.lb[3]` - `r SMD_S_LMA_ARRIVE$subgroup_analysis$ci.ub[3]`          |                            \-                             |
|                    \-                    |  *16-19 criteria met*   |     `r SMD_S_LMA_ARRIVE$subgroup_analysis$beta[4]`      |          `r SMD_S_LMA_ARRIVE$subgroup_analysis$ci.lb[4]` - `r SMD_S_LMA_ARRIVE$subgroup_analysis$ci.ub[4]`          |                            \-                             |

### 5.1.2 Outcome 2: Cognition

##### 5.1.2.1 Sex

Figure 5.1.2.1 displays the estimates for the pooled SMD's when comparisons are stratified by sex of the animal. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by sex, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.2.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_cog_sex <- plot_subgroup_analysis(df, "TvC", "Cognition", "Sex", 0.5)
```

`r SMD_S_cog_sex$subgroup_rma_summary[SMD_S_cog_sex$subgroup_rma_summary$Sex == "Not reported", "k"]` comparisons did not report the sex of the animals used within the experimental cohort. `r SMD_S_cog_sex$subgroup_rma_summary[SMD_S_cog_sex$subgroup_rma_summary$Sex == "Male", "k"]` comparisons used cohorts of only male animals and `r SMD_S_cog_sex$subgroup_rma_summary[SMD_S_cog_sex$subgroup_rma_summary$Sex == "Female", "k"]` comparisons used cohorts of only female animals. There were `r SMD_S_cog_sex$subgroup_rma_summary[SMD_S_cog_sex$subgroup_rma_summary$Sex == "Mixed male and female", "k"]` comparisons using cohorts of both male and female animals.

The pooled SMD estimate for male animals was `r SMD_S_cog_sex$subgroup_rma_summary[SMD_S_cog_sex$subgroup_rma_summary$Sex == "Male", "SMD"]`, for females `r SMD_S_cog_sex$subgroup_rma_summary[SMD_S_cog_sex$subgroup_rma_summary$Sex == "Female", "SMD"]`, and for mixed cohorts `r SMD_S_cog_sex$subgroup_rma_summary[SMD_S_cog_sex$subgroup_rma_summary$Sex == "Mixed male and female", "SMD"]`.

##### 5.1.2.2 Category of disease induction

Figure 5.1.2.2 displays the estimates for the pooled SMD's when comparisons are stratified by the category of disease induction. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by category of disease induction, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.2.2**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_cog_CatDisInd <- plot_subgroup_analysis(df, "TvC", "Cognition", "CategoryDiseaseInduction", 0.5)
```

`r SMD_S_cog_CatDisInd$subgroup_rma_summary[SMD_S_cog_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Pharmacological (e.g. psychostimulants, NMDA antagonists)", "k"]` comparisons used pharmacological methods to induce the disease model. `r SMD_S_cog_CatDisInd$subgroup_rma_summary[SMD_S_cog_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Genetic (e.g. DISC1 KO, DAT KO, D2R overexpression)", "k"]` comparisons used genetic methods to induce the disease model.

The pooled SMD estimate for comparisons using pharmacological methods to induce the disease model was `r SMD_S_cog_CatDisInd$subgroup_rma_summary[SMD_S_cog_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Pharmacological (e.g. psychostimulants, NMDA antagonists)", "SMD"]`, and for comparisons using genetic methods to induce the disease model `r SMD_S_cog_CatDisInd$subgroup_rma_summary[SMD_S_cog_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Genetic (e.g. DISC1 KO, DAT KO, D2R overexpression)", "SMD"]`.

##### 5.1.2.3 Route of intervention administration

Figure 5.1.2.3 displays the estimates for the pooled SMD's when comparisons are stratified by the administration route of the intervention. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by administration route of the intervention, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.2.3**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_cog_AdminRoute <- plot_subgroup_analysis(df, "TvC", "Cognition", "InterventionAdministrationRoute", 0.5)
```

`r SMD_S_cog_AdminRoute$subgroup_rma_summary[SMD_S_cog_AdminRoute$subgroup_rma_summary$InterventionAdministrationRoute == "Intraperitoneal (IP) injection", "k"]` comparisons administered the TAAR1 agonist intraperitoneally. `r SMD_S_cog_AdminRoute$subgroup_rma_summary[SMD_S_cog_AdminRoute$subgroup_rma_summary$InterventionAdministrationRoute == "Oral administration/gavage", "k"]` comparisons administered the TAAR1 agonist orally.

The pooled SMD estimate for experiments administering the TAAR1 agonist intraperitoneally was `r SMD_S_cog_AdminRoute$subgroup_rma_summary[SMD_S_cog_AdminRoute$subgroup_rma_summary$InterventionAdministrationRoute == "Intraperitoneal (IP) injection", "SMD"]`, and for experiments administering the TAAR1 agonist orally `r SMD_S_cog_AdminRoute$subgroup_rma_summary[SMD_S_cog_AdminRoute$subgroup_rma_summary$InterventionAdministrationRoute == "Oral administration/gavage", "SMD"]`.

##### 5.1.2.4 Prophylactic or therapeutic intervention

In this iteration of the review, all relevant comparisons administered the TAAR1 agonist after induction of the disease model. Therefore, no subgroup analyses were conducted for this variable.

##### 5.1.2.5 Duration of treatment period

In this iteration of the review, all relevant comparisons administered the TAAR1 agonist for \< 1 week. Therefore, no subgroup analyses were conducted for this variable.

##### 5.1.2.6 The intervention administered

Figure 5.1.2.6 displays the estimates for the pooled SMD's when comparisons are stratified by the intervention administered. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by the intervention administered, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.2.6**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_cog_Drug <- plot_subgroup_analysis(df, "TvC", "Cognition", "DrugName", 0.5)
```

The TAAR1 agonist SEP-363856 (Ultaront) was administered in `r SMD_S_LMA_Drug$subgroup_rma_summary[SMD_S_LMA_Drug$subgroup_rma_summary$DrugName == "SEP-363856", "k"]` experiments. `r SMD_S_cog_Drug$subgroup_rma_summary[SMD_S_cog_Drug$subgroup_rma_summary$DrugName == "RO5203648", "k"]` experiments administered the TAAR1 agonist RO5203648, and `r SMD_S_cog_Drug$subgroup_rma_summary[SMD_S_cog_Drug$subgroup_rma_summary$DrugName == "RO5256390", "k"]` experiments administered the TAAR1 agonist RO5256390.

The pooled SMD estimate for experiments administering the TAAR1 agonist SEP-363856 was `r SMD_S_cog_Drug$subgroup_rma_summary[SMD_S_cog_Drug$subgroup_rma_summary$DrugName == "SEP-363856", "SMD"]`, for experiments administering the TAAR1 agonist RO5203648 `r SMD_S_cog_Drug$subgroup_rma_summary[SMD_S_cog_Drug$subgroup_rma_summary$DrugName == "RO5203648", "SMD"]`, and for experiments administering the TAAR1 agonist RO5256390 `r SMD_S_cog_Drug$subgroup_rma_summary[SMD_S_cog_Drug$subgroup_rma_summary$DrugName == "RO5256390", "SMD"]`.

##### 5.1.2.7 The efficacy of the drug (i.e. whether the drug is a partial or full agonist)

In this iteration of the review, all relevant comparisons administered the TAAR1 agonists with partial agonist activity. Therefore, no subgroup analyses were conducted for this variable.

##### 5.1.2.8 The selectivity of the drug

Figure 5.1.2.8 displays the estimates for the pooled SMD's when comparisons are stratified by the selectivity of the intervention administered. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by intervention selectivity, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.2.8**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_cog_DrugSelectivity <- plot_subgroup_analysis(df, "TvC", "Cognition", "Selectivity", 0.5)
```

TAAR1 agonists with high selectivity were used in `r SMD_S_cog_DrugSelectivity$subgroup_rma_summary[SMD_S_cog_DrugSelectivity$subgroup_rma_summary$Selectivity == "High", "k"]` experiments. TAAR1 drugs with additional agonist activity at serotonin 5HT1A receptors were used in `r SMD_S_cog_DrugSelectivity$subgroup_rma_summary[SMD_S_cog_DrugSelectivity$subgroup_rma_summary$Selectivity == "Low (5HT1A partial agonism)", "k"]` experiments.

The pooled SMD estimate for experiments administering TAAR1 agonists with high selectivity was `r SMD_S_cog_DrugSelectivity$subgroup_rma_summary[SMD_S_cog_DrugSelectivity$subgroup_rma_summary$Selectivity == "High", "SMD"]`, and for experiments administering TAAR1 agonists with low selectivity `r SMD_S_cog_DrugSelectivity$subgroup_rma_summary[SMD_S_cog_DrugSelectivity$subgroup_rma_summary$Selectivity == "Low (5HT1A partial agonism)", "SMD"]`.

#### 5.1.2.9 Potency of intervention

The pEC50 value of each drug was used to measure potency. The pEC50 value is the negative logarithm (to base 10) of the EC50 value. Higher pEC50 values indicate higher potency (as they indicate a lower EC50). Figure x displays a visualisation of the meta-regression using the pEC50 value as an explanatory variable. Dashed lines represent the 95% confidence interval of the regression line. The dotted lines represent the 95% prediction interval. Raw data is plotted with 'bubble' size adjusted according to effect size precision.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_potency <- metaregression_analysis(df, "TvC", "Cognition", "pE50", 0.5)
```

**Figure 5.1.2.9**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_cog_potency$regression_plot
```

The estimate for $\theta$ was `r SMD_S_cog_potency$metaregression_summary$beta[1]`. This gives the predicted SMD when the pEC50 of the intervention is 0. Note that this should be interpreted with caution; since the logarithm of zero is undefined (it tends towards negative infinity), a pEC50 value cannot be 0 unless the EC50 is 1 mol/L. The estimate for $\theta$ can be interpreted as the estimated SMD when the EC50 is 1 mol/L (1000mM), which signifies extremely low potency.

The estimate for $\beta$ was `r SMD_S_cog_potency$metaregression_summary$beta[2]`. This represents the predicted regression weight for the pEC50 of the intervention.

#### 5.1.2.10 Dose of intervention

In this iteration of the review, the TAAR1 agonists administered in 'simple intervention' experiments (ordered by number of experiments) were; **`r drugs <- df %>% filter(SortLabel == "TvC") %>% filter(outcome_type == "Cognition") %>% group_by(DrugName) %>% summarise(count = n()) %>% arrange(desc(count)) %>% pull(DrugName); if (length(drugs) > 1) {paste(paste(head(drugs, -1), collapse = ", "), "and", tail(drugs, 1))} else {drugs}`**. Meta-regression using the administered dose as an explanatory variable was first conducted individually for each drug/intervention. This approach accounts for varying mechanisms of action, pharmacodynamics, and pharmacokinetics of each drug, ensuring that the dose effect of one intervention is not masked by aggregate data.

In the following plots, dashed lines represent the 95% confidence interval of the regression line and dotted lines represent the 95% prediction interval. Raw data is plotted with point size adjusted according to effect size precision.

##### 5.1.2.10.1 SEP-363856 (Ultaront)

Figure 5.1.2.10.1 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in Cognition to varying doses of SEP-363856 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_SEP363856_dose <- metaregression_analysis_by_drug(df, "TvC", "Cognition", "SEP-363856", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.2.10.1**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_cog_SEP363856_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_cog_SEP363856_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_cog_SEP363856_dose$metaregression_summary$beta[2]`.

##### 5.1.2.10.2 RO5203648

For 4 comparisons of RO5203648 reporting cognitive outcomes a single dose was used, with outcomes measured at different times, so metaregression is not possible.

##### 5.1.2.10.3 RO5166017

No cognitive outcomes were reported for RO5166017.

##### 5.1.2.10.4 RO5263397

No cognitive outcomes were reported for RO5263397.

##### 5.1.2.10.5 RO5256390

Figure 5.1.2.10.5 provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in Cognition to varying doses of RO5256390 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_RO5256390_dose <- metaregression_analysis_by_drug(df, "TvC", "Cognition", "RO5256390", "DoseOfIntervention_mgkg", 0.5)
```

**Figure 5.1.2.10.5**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_cog_RO5256390_dose$regression_plot
```

##### 5.1.2.10.6 LK000764

No cognitive outcomes were reported for LK000764.

##### 5.1.2.10.7 Compound 50B

No cognitive outcomes were reported for Compound 50B.

##### 5.1.2.10.8 Compound 50A

No cognitive outcomes were reported for Compound 50A.

##### 5.1.2.10.9 RO5073012

No cognitive outcomes were reported for RO5073012.

##### 5.1.2.10.10 AP163

No cognitive outcomes were reported for AP163.

##### 5.1.2.10.11 Standardised dose

We then sought evidence of a dose response relationship across all drugs. To do this, we conducted meta-regression using a standardised dose variable. This variable quantifies the administered dose as a multiple of the drug's EC50, indicating how many times the dose administered was greater (or lesser) than the concentration needed to achieve half-maximal effect. For example, if a drug's dose is twice its EC50, the standardized dose would be 2, indicating that the dose is twice the concentration needed to achieve half-maximal effect.

The standardised dose was calculated by dividing the log-transformed dose of the intervention (in mg/kg) by the product of the intervention's EC50 (in moles) and the Molar mass of the drug (in mg/mol):

$$
\frac{\log(\text{Dose of Intervention (mg/kg)})}{(\text{Molar Mass (g/mol)} \times 1000) \times (\frac{\text{EC50 (micromoles)}}{1000000})}
$$

**This is a simplified approximation based on the reasoning that if drug actions are mediated through the TAAR1 receptor, and drug efficacy is reflected in the respective EC50 values, then theoretically drugs should exhibit similar effects when acting at their respective EC50.**

The actual concentration of a drug at the receptor site is influenced by several variables, including dosage, administration route, elimination half-life, and first-pass metabolism (in case of oral administration). Incorporating all these factors accurately would necessitate a detailed pharmacokinetic model, which falls outside the scope of this review. Consequently, we assume uniformity across experiments in terms of (i) volume of distribution, (ii) first-pass metabolism, (iii) blood-brain barrier permeability, and (iv) experimental design, especially regarding the timing of peak drug concentration (where we assume that experiments were designed to be done at a time when the drug was near peak concentration).

Figure x provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in Cognition to varying standardised doses of TAAR1 agonists. As before, dashed lines represent the 95% confidence interval of the regression line and dotted lines represent the 95% prediction interval. Raw data is plotted with point size adjusted according to effect size precision.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_StandardDose <- metaregression_analysis(df, "TvC", "Cognition", "StandardisedDose", 0.5)
```

**Figure 5.1.2.10.11**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_cog_StandardDose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_cog_StandardDose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_cog_StandardDose$metaregression_summary$beta[2]`.

##### 5.1.2.11 SYRCLE RoB assessment

Figure 5.1.2.11 displays the estimates for the pooled SMD's when comparisons are stratified by how many of the SYRCLE risk of bias assessment criteria (of which there are 10) that the experiment met. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by SYRCLE RoB assessment, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.2.11**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_cog_SYRCLERoB <- plot_subgroup_analysis(df, "TvC", "Cognition", "RoBScore", 0.5)
```

`r SMD_S_cog_SYRCLERoB$subgroup_rma_summary[SMD_S_cog_SYRCLERoB$subgroup_rma_summary$RoBScore == "0 criteria met", "k"]` experiments met none of the SYRCLE Risk of Bias criteria. `r SMD_S_cog_SYRCLERoB$subgroup_rma_summary[SMD_S_cog_SYRCLERoB$subgroup_rma_summary$RoBScore == "1 criteria met", "k"]` experiments met one of the SYRCLE Risk of Bias criteria. No studies met more than one of the SYRCLE Risk of Bias criteria.

The pooled SMD estimate for experiments that met none of the SYRCLE Risk of Bias criteria was `r SMD_S_cog_SYRCLERoB$subgroup_rma_summary[SMD_S_cog_SYRCLERoB$subgroup_rma_summary$RoBScore == "0 criteria met", "SMD"]`, and for experiments that met one of the SYRCLE Risk of Bias criteria `r SMD_S_cog_SYRCLERoB$subgroup_rma_summary[SMD_S_cog_SYRCLERoB$subgroup_rma_summary$RoBScore == "1 criteria met", "SMD"]`.

Figure 5.1.2.11 displays the estimates for the pooled SMD's when comparisons are stratified by this categorisation that the experiment met. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by SyRCLE Risk of Bias, is displayed as a diamond shape at the bottom of the plot.

##### 5.1.2.12 ARRIVE reporting quality guidelines

Experiments were categorised based on the number of ARRIVE guidelines (of which there are 23) met. The categorisation was as follows: Experiments meeting 3 or fewer criteria were labeled as "A: \< 3 criteria met"; those meeting 4 to 7 criteria were labeled "B: 4-7 criteria met"; for 8 to 11 criteria, "C: 8-11 criteria met"; for 12 to 15 criteria, "D: 12-15 criteria met"; for 16 to 19 criteria, "E: 16-19 criteria met"; and experiments meeting more than 19 criteria were labeled as "F: \> 20 criteria met".

Figure 5.1.2.12 displays the estimates for the pooled SMD's when comparisons are stratified by this categorisation that the experiment met. Whiskers indicate the 95% confidence interval of each estimate. The overall pooled SMD, not stratified by ARRIVE reporting quality guidelines, is displayed as a diamond shape at the bottom of the plot.

**Figure 5.1.2.12**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide', fig.width=9, fig.height=5}
SMD_S_cog_ARRIVE <- plot_subgroup_analysis(df, "TvC", "Cognition", "ARRIVEScoreCat", 0.5)
```

`r SMD_S_cog_ARRIVE$subgroup_rma_summary[SMD_S_cog_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "C: 8-11 criteria met", "k"]` experiments met between 8-11 of the ARRIVE reporting quality criteria. No studies met less than 8 or more than 19 of the ARRIVE reporting quality criteria. `r SMD_S_cog_ARRIVE$subgroup_rma_summary[SMD_S_cog_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "D: 12-15 criteria met", "k"]` experiments met between 12-15, and `r SMD_S_cog_ARRIVE$subgroup_rma_summary[SMD_S_cog_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "E: 16-19 criteria met", "k"]` experiments met between 16-19 of the ARRIVE reporting quality criteria. No studies met less than 8 or more than 19 of the ARRIVE reporting quality criteria.

The pooled SMD estimate for experiments that met between 8-11 of the ARRIVE reporting quality criteria was `r SMD_S_cog_ARRIVE$subgroup_rma_summary[SMD_S_cog_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "C: 8-11 criteria met", "SMD"]`, and for experiments that met between 12-15 of the ARRIVE reporting quality criteria `r SMD_S_cog_ARRIVE$subgroup_rma_summary[SMD_S_cog_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "D: 12-15 criteria met", "SMD"]`, and for experiments that met between 16-19 of the ARRIVE reporting quality criteria `r SMD_S_cog_ARRIVE$subgroup_rma_summary[SMD_S_cog_ARRIVE$subgroup_rma_summary$ARRIVEScoreCat == "E: 16-19 criteria met", "SMD"]`.

##### 5.1.2.13 Heterogeneity explained by covariates (simple interventions on cognition)

The table below shows which of the covariates, if any, explain some of the heterogeneity observed in the effect sizes of the effect of TAAR1 agonists on cognition. We present marginal R^2^, which measures the proportion of variance explained by including moderators in the model.

|              Moderator              |        Category         |                         $\beta$                         |                                                       95% CI                                                        |                       Marginal R^2^                       |
|:-------------:|:-------------:|:-------------:|:-------------:|:-------------:|
|           Overall effect            |           \-            |                  `r SMD_S_cog$beta[1]`                  |                                      `r SMD_S_cog$ci.lb` - `r SMD_S_cog$ci.ub`                                      |                            \-                             |
|                 Sex                 |           \-            |                           \-                            |                                                         \-                                                          |       `r r2_ml(SMD_S_cog_sex$subgroup_analysis)[1]`       |
|                 \-                  |        *Female*         |       `r SMD_S_cog_sex$subgroup_analysis$beta[1]`       |             `r SMD_S_cog_sex$subgroup_analysis$ci.lb[1]` - `r SMD_S_cog_sex$subgroup_analysis$ci.ub[1]`             |                            \-                             |
|                 \-                  |         *Male*          |       `r SMD_S_cog_sex$subgroup_analysis$beta[2]`       |             `r SMD_S_cog_sex$subgroup_analysis$ci.lb[2]` - `r SMD_S_cog_sex$subgroup_analysis$ci.ub[2]`             |                            \-                             |
|                 \-                  | *Mixed male and female* |       `r SMD_S_cog_sex$subgroup_analysis$beta[3]`       |             `r SMD_S_cog_sex$subgroup_analysis$ci.lb[3]` - `r SMD_S_cog_sex$subgroup_analysis$ci.ub[3]`             |                            \-                             |
| Category of disease model induction |           \-            |                           \-                            |                                                         \-                                                          |    `r r2_ml(SMD_S_cog_CatDisInd$subgroup_analysis)[1]`    |
|                 \-                  |        *Genetic*        |    `r SMD_S_cog_CatDisInd$subgroup_analysis$beta[1]`    |       `r SMD_S_cog_CatDisInd$subgroup_analysis$ci.lb[1]` - `r SMD_S_cog_CatDisInd$subgroup_analysis$ci.ub[1]`       |                            \-                             |
|                 \-                  |    *Pharmacological*    |    `r SMD_S_cog_CatDisInd$subgroup_analysis$beta[2]`    |       `r SMD_S_cog_CatDisInd$subgroup_analysis$ci.lb[2]` - `r SMD_S_cog_CatDisInd$subgroup_analysis$ci.ub[2]`       |                            \-                             |
|        Administration route         |           \-            |                           \-                            |                                                         \-                                                          |   `r r2_ml(SMD_S_cog_AdminRoute$subgroup_analysis)[1]`    |
|                 \-                  |    *Intraperitoneal*    |   `r SMD_S_cog_AdminRoute$subgroup_analysis$beta[1]`    |      `r SMD_S_cog_AdminRoute$subgroup_analysis$ci.lb[1]` - `r SMD_S_cog_AdminRoute$subgroup_analysis$ci.ub[1]`      |                            \-                             |
|                 \-                  |         *Oral*          |   `r SMD_S_cog_AdminRoute$subgroup_analysis$beta[2]`    |      `r SMD_S_cog_AdminRoute$subgroup_analysis$ci.lb[2]` - `r SMD_S_cog_AdminRoute$subgroup_analysis$ci.ub[2]`      |                            \-                             |
|      Intervention administered      |           \-            |                           \-                            |                                                         \-                                                          |      `r r2_ml(SMD_S_cog_Drug$subgroup_analysis)[1]`       |
|                 \-                  |       *RO5203648*       |      `r SMD_S_cog_Drug$subgroup_analysis$beta[1]`       |            `r SMD_S_cog_Drug$subgroup_analysis$ci.lb[1]` - `r SMD_S_cog_Drug$subgroup_analysis$ci.ub[1]`            |                            \-                             |
|                 \-                  |       *RO5256390*       |      `r SMD_S_cog_Drug$subgroup_analysis$beta[2]`       |            `r SMD_S_cog_Drug$subgroup_analysis$ci.lb[2]` - `r SMD_S_cog_Drug$subgroup_analysis$ci.ub[2]`            |                            \-                             |
|                 \-                  | *SEP-363856 (Ultaront)* |      `r SMD_S_cog_Drug$subgroup_analysis$beta[3]`       |            `r SMD_S_cog_Drug$subgroup_analysis$ci.lb[3]` - `r SMD_S_cog_Drug$subgroup_analysis$ci.ub[3]`            |                            \-                             |
|          Drug selectivity           |           \-            |                           \-                            |                                                         \-                                                          | `r r2_ml(SMD_S_cog_DrugSelectivity$subgroup_analysis)[1]` |
|                 \-                  |         *High*          | `r SMD_S_cog_DrugSelectivity$subgroup_analysis$beta[1]` | `r SMD_S_cog_DrugSelectivity$subgroup_analysis$ci.lb[1]` - `r SMD_S_cog_DrugSelectivity$subgroup_analysis$ci.ub[1]` |                            \-                             |
|                 \-                  |          *Low*          | `r SMD_S_cog_DrugSelectivity$subgroup_analysis$beta[2]` | `r SMD_S_cog_DrugSelectivity$subgroup_analysis$ci.lb[2]` - `r SMD_S_cog_DrugSelectivity$subgroup_analysis$ci.ub[2]` |                            \-                             |
|            Risk of Bias             |           \-            |                           \-                            |                                                         \-                                                          |    `r r2_ml(SMD_S_cog_SYRCLERoB$subgroup_analysis)[1]`    |
|                 \-                  |    *0 criteria met*     |    `r SMD_S_cog_SYRCLERoB$subgroup_analysis$beta[1]`    |       `r SMD_S_cog_SYRCLERoB$subgroup_analysis$ci.lb[1]` - `r SMD_S_cog_SYRCLERoB$subgroup_analysis$ci.ub[1]`       |                            \-                             |
|                 \-                  |    *1 criteria met*     |    `r SMD_S_cog_SYRCLERoB$subgroup_analysis$beta[2]`    |       `r SMD_S_cog_SYRCLERoB$subgroup_analysis$ci.lb[2]` - `r SMD_S_cog_SYRCLERoB$subgroup_analysis$ci.ub[2]`       |                            \-                             |
|          Reporting quality          |           \-            |                           \-                            |                                                         \-                                                          |     `r r2_ml(SMD_S_cog_ARRIVE$subgroup_analysis)[1]`      |
|                 \-                  |   *8-11 criteria met*   |     `r SMD_S_cog_ARRIVE$subgroup_analysis$beta[1]`      |          `r SMD_S_cog_ARRIVE$subgroup_analysis$ci.lb[1]` - `r SMD_S_cog_ARRIVE$subgroup_analysis$ci.ub[1]`          |                            \-                             |
|                 \-                  |  *12-15 criteria met*   |     `r SMD_S_cog_ARRIVE$subgroup_analysis$beta[2]`      |          `r SMD_S_cog_ARRIVE$subgroup_analysis$ci.lb[2]` - `r SMD_S_cog_ARRIVE$subgroup_analysis$ci.ub[2]`          |                            \-                             |
|                 \-                  |  *16-19 criteria met*   |     `r SMD_S_cog_ARRIVE$subgroup_analysis$beta[3]`      |          `r SMD_S_cog_ARRIVE$subgroup_analysis$ci.lb[3]` - `r SMD_S_cog_ARRIVE$subgroup_analysis$ci.ub[3]`          |                            \-                             |

# 6. Meta-regression analyses

For each outcome, the variables of interest for meta-regression analyses are;

-   **The potency of the intervention**

-   **The dose of the intervention administered**

## 6.1 Meta-regression analyses for simple interventions

### 6.1.2 Cognition

#### 6.1.2.1 Potency of intervention

The pEC50 value of each drug was again used to measure potency. Higher pEC50 values indicate higher potency (as they indicate a lower EC50). Figure x displays a visualisation of the meta-regression using the pEC50 value as an explanatory variable. Dashed lines represent the 95% confidence interval of the regression line. The dotted lines represent the 95% prediction interval. Raw data is plotted with 'bubble' size adjusted according to effect size precision.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_potency <- metaregression_analysis(df, "TvC", "Cognition", "pE50", 0.5)
```

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_cog_potency$regression_plot
```

The estimate for $\theta$ was `r SMD_S_cog_potency$metaregression_summary$beta[1]`. This gives the predicted SMD when the pEC50 of the intervention is 0. Note that this should be interpreted with caution; since the logarithm of zero is undefined (it tends towards negative infinity), a pEC50 value cannot be 0 unless the EC50 is 1 mol/L. The estimate for $\theta$ can be interpreted as the estimated SMD when the EC50 is 1 mol/L (1000mM), which signifies extremely low potency.

The estimate for $\beta$ was `r SMD_S_cog_potency$metaregression_summary$beta[2]`. This represents the predicted regression weight for the pEC50 of the intervention.

#### 6.1.2.2 Dose of intervention

In this iteration of the review, the TAAR1 agonists administered in 'simple intervention' experiments (ordered by number of experiments) were; **`r drugs <- df %>% filter(SortLabel == "TvC") %>% filter(outcome_type == "Cognition") %>% group_by(DrugName) %>% summarise(count = n()) %>% arrange(desc(count)) %>% pull(DrugName); if (length(drugs) > 1) {paste(paste(head(drugs, -1), collapse = ", "), "and", tail(drugs, 1))} else {drugs}`**. Meta-regression using the administered dose as an explanatory variable was first conducted individually for each drug/intervention. This approach accounts for varying mechanisms of action, pharmacodynamics, and pharmacokinetics of each drug, ensuring that the dose effect of one intervention is not masked by aggregate data.

##### 6.1.2.2.1 SEP-363856 (Ultaront)

Figure x provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in cognition to varying doses of SEP-363856 (in mg/kg).

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_SEP363856_dose <- metaregression_analysis_by_drug(df, "TvC", "Cognition", "SEP-363856", "DoseOfIntervention_mgkg", 0.5)
```

**Figure x**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_cog_SEP363856_dose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_cog_SEP363856_dose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_cog_SEP363856_dose$metaregression_summary$beta[2]`.

##### 6.1.2.2.2 RO5203648

In this iteration of the review, all relevant comparisons used the same dose of RO5203648 (1 mg/kg). Therefore, meta-regression on the dose on intervention was not conducted for this drug.

##### 6.1.2.2.3 RO5256390

In this iteration of the review, there was insufficient data to perform meta-regression on the dose on intervention for RO5256390 (only a single data point for each dose of RO5256390 administered)

##### 6.1.2.2.4 Standardised dose

As for locomotor activity, we then sought evidence of a dose response relationship across all drugs using the standardised dose variable.

Figure x provides a visualisation of the meta-regression analysis predicting the response, measured as the Standardized Mean Difference (SMD), in cognition to varying standardised doses of TAAR1 agonists. As before, dashed lines represent the 95% confidence interval of the regression line and dotted lines represent the 95% prediction interval. Raw data is plotted with point size adjusted according to effect size precision.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_StandardDose <- metaregression_analysis(df, "TvC", "Cognition", "StandardisedDose", 0.5)
```

**Figure x**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE,}
SMD_S_cog_StandardDose$regression_plot
```

The estimate for $\theta$ was `r SMD_S_cog_StandardDose$metaregression_summary$beta[1]`. The estimate for $\beta$ was `r SMD_S_cog_StandardDose$metaregression_summary$beta[2]`.

# 7. Sensitivity Analyses

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
options(scipen = 100, digits = 2)
```

We examine the robustness of the findings for the primary outcome by performing the following sensitivity analyses:

**1. Restricting the analysis to studies with low risk of bias**

**2. Imputed rho values of 0.2 and 0.8**

**3. NMD analysis**

## 7.1 Sensitivity analyses for simple interventions

### 7.1.1 Locomotor activity

#### 7.1.1.1 Studies with low overall risk of bias

In this iteration of the review, 0 studies had an overall low risk of bias. A study was categorised as having a low risk of bias if it met at least half of the SYRCLE checklist criteria. Therefore, no sensitivity analysis was performed.

#### 7.1.1.2 Imputed rho values of 0.2 and 0.8

In the previous analyses for the effect of TAAR1 agonists on locomotor activity, we imputed a $\rho$ value of 0.5. Here, we examine the effect of imputing $\rho$ values of 0.2 and 0.8.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_rho0.2 <- run_ML_SMD(df, "TvC", "Locomotor activity", 0.2)
```

**When the** $\rho$ value is assumed to be 0.2, the TAAR1 interventions had a pooled effect on locomotor activity of **SMD = `r SMD_S_LMA_rho0.2[["beta"]]`** (95% CI: `r SMD_S_LMA_rho0.2[["ci.lb"]]` to `r SMD_S_LMA_rho0.2[["ci.ub"]]`) with a prediction interval of `r predict(SMD_S_LMA_rho0.2)$pi.lb` to `r predict(SMD_S_LMA_rho0.2)$pi.ub`.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_LMA_rho0.8 <- run_ML_SMD(df, "TvC", "Locomotor activity", 0.8)
```

**When the** $\rho$ value is assumed to be 0.8, the TAAR1 interventions had a pooled effect on locomotor activity of **SMD = `r SMD_S_LMA_rho0.8[["beta"]]`** (95% CI: `r SMD_S_LMA_rho0.8[["ci.lb"]]` to `r SMD_S_LMA_rho0.8[["ci.ub"]]`) with a prediction interval of `r predict(SMD_S_LMA_rho0.8)$pi.lb` to `r predict(SMD_S_LMA_rho0.8)$pi.ub`.

For reference the pooled effect size when rho is assumed to be 0.5 is `r SMD_S_LMA[["beta"]]` (95% CI: `r SMD_S_LMA[["ci.lb"]]` to `r SMD_S_LMA[["ci.ub"]]`).

#### 7.1.1.3 NMD

For locomotor activity, an NMD was calculable for `r df_S_LMA %>% filter(NMD_possible == "TRUE") %>% nrow()` out of `r nrow(df_S_LMA)` comparisons, i.e. `r ((df_S_LMA %>% filter(NMD_possible == "TRUE") %>% nrow())/(nrow(df_S_LMA)))*100` % of comparisons.

The effect of administering a TAAR1 agonist on locomotor activity in animals using NMD as the effect size is shown in Figure x. The pooled estimate for NMD across all individual comparisons is displayed as a diamond shape at the bottom of the plot. Dotted lines indicate the prediction interval of the pooled estimate.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
NMD_S_LMA <- run_ML_NMD(df, "TvC", "Locomotor activity", 0.5)
```

**Figure x**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
forest_metafor_NMD(NMD_S_LMA, "locomotor hyperactivity")
```

For simple interventions, TAAR1 interventions had a pooled effect on locomotor activity of NMD = `r NMD_S_LMA[["beta"]]` (95% CI: `r NMD_S_LMA[["ci.lb"]]` to `r NMD_S_LMA[["ci.ub"]]`) with a prediction interval of `r predict(NMD_S_LMA)$pi.lb` to `r predict(NMD_S_LMA)$pi.ub`. For reference the pooled effect size for SMD was `r SMD_S_LMA[["beta"]]` (95% CI: `r SMD_S_LMA[["ci.lb"]]` to `r SMD_S_LMA[["ci.ub"]]`).

### 7.1.2 Cognition

#### 7.1.2.1 Studies with low overall risk of bias

In this iteration of the review, 0 studies had an overall low risk of bias. A study was categorised as having a low risk of bias if it met at least half of the SYRCLE checklist criteria. Therefore, no sensitivity analysis was performed.

#### 7.1.2.2 Imputed rho values of 0.2 and 0.8

In the previous analyses for the effect of TAAR1 agonists on cognition, we imputed a $\rho$ value of 0.5. Here, we examine the effect of imputing $\rho$ values of 0.2 and 0.8.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_rho0.2 <- run_ML_SMD(df, "TvC", "Cognition", 0.2)
```

**When the** $\rho$ value is assumed to be 0.2, the TAAR1 interventions had a pooled effect on cognition of **SMD = `r SMD_S_cog_rho0.2[["beta"]]`** (95% CI: `r SMD_S_cog_rho0.2[["ci.lb"]]` to `r SMD_S_cog_rho0.2[["ci.ub"]]`) with a prediction interval of `r predict(SMD_S_cog_rho0.2)$pi.lb` to `r predict(SMD_S_cog_rho0.2)$pi.ub`.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
SMD_S_cog_rho0.8 <- run_ML_SMD(df, "TvC", "Cognition", 0.8)
```

**When the** $\rho$ value is assumed to be 0.8, the TAAR1 interventions had a pooled effect on cognition of **SMD = `r SMD_S_cog_rho0.8[["beta"]]`** (95% CI: `r SMD_S_cog_rho0.8[["ci.lb"]]` to `r SMD_S_cog_rho0.8[["ci.ub"]]`) with a prediction interval of `r predict(SMD_S_cog_rho0.8)$pi.lb` to `r predict(SMD_S_cog_rho0.8)$pi.ub`.

For reference the pooled effect size when rho is assumed to be 0.5 is `r SMD_S_cog[["beta"]]` (95% CI: `r SMD_S_cog[["ci.lb"]]` to `r SMD_S_cog[["ci.ub"]]`).

#### 7.1.2.3 NMD

For cognition, an NMD was calculable for `r df_S_cog %>% filter(NMD_possible == "TRUE") %>% nrow()` out of `r nrow(df_S_cog)` comparisons, i.e. `r ((df_S_cog %>% filter(NMD_possible == "TRUE") %>% nrow())/(nrow(df_S_cog)))*100` % of comparisons.

The effect of administering a TAAR1 agonist on cognition in animals using NMD as the effect size is shown in Figure x. The pooled estimate for NMD across all individual comparisons is displayed as a diamond shape at the bottom of the plot. Dotted lines indicate the prediction interval of the pooled estimate.

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE, results='hide'}
NMD_S_cog <- run_ML_NMD(df, "TvC", "Cognition", 0.5)
```

**Figure x**

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
forest_metafor_NMD(NMD_S_cog, "Cognition")
```

For simple interventions, TAAR1 interventions had a pooled effect on cognition of NMD = `r NMD_S_cog[["beta"]]` (95% CI: `r NMD_S_cog[["ci.lb"]]` to `r NMD_S_cog[["ci.ub"]]`) with a prediction interval of `r predict(NMD_S_cog)$pi.lb` to `r predict(NMD_S_cog)$pi.ub`. For reference the pooled effect size for SMD was `r SMD_S_cog[["beta"]]` (95% CI: `r SMD_S_cog[["ci.lb"]]` to `r SMD_S_cog[["ci.ub"]]`).

# 8. Reporting bias/small study effects

<!--# why running it on the NMD instead of SMD? -->

<!--# as discussed with Georgia, this should be done on the sample size rather than on the SE -->

<!--# also, i would remove the bubble plots -->

## 8.1 Egger regression

Small studies effects using modified Egger's regression

```{r warning=FALSE, eval = TRUE, echo = FALSE}
run_sse_plot(df)
#run_sse_NMD(df)
```

Egger regression based on `r run_sse_NMD(df)[["k"]]` studies of Simple interventions where Locomotor activity was measured and NMD was evaluable showed a coefficient for a small study effect of `r run_sse_NMD(df)[["beta"]][2]` (95% CI: `r run_sse_NMD(df)[["ci.lb"]][2]` to `r run_sse_NMD(df)[["ci.ub"]][2]`; p = `r ifelse(run_sse_NMD(df)[["pval"]][2] < 0.001, "<0.001", sprintf("%.3f", run_sse_NMD(df)[["pval"]][2]))`) in the context of a baseline estimate of effect of `r run_sse_NMD(df)[["beta"]][1]` (95% CI: `r run_sse_NMD(df)[["ci.lb"]][1]` to `r run_sse_NMD(df)[["ci.ub"]][1]`; p = `r ifelse(run_sse_NMD(df)[["pval"]][2] < 0.001, "<0.001", sprintf("%.3f", run_sse_NMD(df)[["pval"]][1]))`).

# 9. Summary of the evidence

|                                 |                                  |                                                           |                                                         |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |                               |
|---------|----------|-----------|-----------|------------------------|------------|
| **Source of evidence**          | **Summary of the association**   | **Bias due to study limitations**                         | **Bias due to reporting bias**                          | **Bias due to indirectedness**                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           | **Bias due to other reasons** |
| Animal and pre-clinical studies |                                  | No studies were of low risk of bias or low reporting bias | Egger Regression showed evidence of small study effects | Bias due to indirectness was assessed as follows. The **Initial organism (Homological validity)** We assessed rodents as having moderate validity as a non primate mammalian species, and all experiments included here were conducted in rodents. Further, `r SMD_S_LMA_CatDisInd$subgroup_rma_summary[SMD_S_LMA_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Genetic (e.g. DISC1 KO, DAT KO, D2R overexpression)", "k"]` studies reporting locomotor activity and `r SMD_S_cog_CatDisInd$subgroup_rma_summary[SMD_S_cog_CatDisInd$subgroup_rma_summary$CategoryDiseaseInduction == "Genetic (e.g. DISC1 KO, DAT KO, D2R overexpression)", "k"]` studies reporting cognition used a genetic manipulation in a gene (DAT) known to be associated with human disease. **Early environment factors inducing transition from initial organism to vulnerable organism (Ontopathogenic validity)** Aside from the genetic models above, no models manipulated early environmental factors. **Triggering factors inducing transition from Vulnerable organism to Pathological organism** were commonly used (e.g. cocaine, amphetamine, PCP) but usually only with short term exposures trigerring increased locomotor activity. It was not possible to assess **Pathological Organism Mechanistic validity** (whether the neurobiological or cognitive mechanisms which operate in human disease could be observed in the animal models used) or **Triggering factors inducing changes in biomarkers (Induction validity)** because these were not assessed. **Therapeutic agents inducing changes in outcome** There was some evidence to support directness in that known antipsychotic drugs had observed efficacy in improving locomotor activity. **Biological markers** There were insufficient studies reporting neuotransmitter levels and no studies reported brain imaging outcomes. **Behavioural manifestations (Ethological validity)** Most studies reported locomotor activity, but `r SMD_S_cog[["k"]]` studies reported some form of cognitive outcome, and in these there was no significant effect of TAAR1 agonists `r SMD_S_cog[["beta"]]` (95% CI: `r SMD_S_cog[["ci.lb"]]` to `r SMD_S_cog[["ci.ub"]]`. |                               |
| Human studies                   |                                  |                                                           |                                                         |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |                               |

### Software used

```{r echo=FALSE}
grateful::cite_packages(output = "paragraph", pkgs = "Session", out.dir = ".")
```
